### 2020-04-14 papers.tex
Capitalise All the Titles in the Table of Contents

\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
\insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}

\insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}

\insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural differences between practical and cognitive presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}

@@

\insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

\insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
\insertmydocument{chapter}{Knowledge and the epistemic function of argumentation -- Commentary on Gasc\'{o}n's Where are dissent and reasons in epistemic justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}

@@

\insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}

@@

\insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the problem of overexpressed premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}

@@

\insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}

\insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}

\insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}

\insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}

@@

\insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}

@@

\insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
\insertmydocument{chapter}{An optimistic perspective on deep disagreement? Commentary on Tindale’s Strange Fish: Belief and the roots of disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}

\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}

@@

\insertmydocument{chapter}{Is there a crisis of dissent and disagreement in argument theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3

@@

\insertmydocument{chapter}{The role of reasoning and arguing in youth democratic participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
\insertmydocument{chapter}{Pictures and Reasoning: visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
\insertmydocument{chapter}{Issues leading to argumentative discussions during family mealtime conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
\insertmydocument{chapter}{Value-based argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16

@@

\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{The semantic mechanisms underlying disagreement. An argumentative semantics approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23

@@

\insertmydocument{chapter}{Arguing Brexit on Twitter: a corpus linguistic study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
\insertmydocument{chapter}{Protagoras’ principles, disagreement and the possibility of error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
\insertmydocument{chapter}{Changing minds through argumentation: Black Pete as a case study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
\insertmydocument{chapter}{The pragma-dialectical view of comparison argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
\insertmydocument{chapter}{The visual rhetoric of iconic photographs as topoi in editorial cartoons: an argumentative analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36

@@

\insertmydocument{chapter}{Representing second-order arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
\insertmydocument{chapter}{Argumentation, dissent, and luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44

@@

\insertmydocument{chapter}{Resolution of deep disagreement: not simply consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47

@@

\insertmydocument{chapter}{Formal specifications for dialogue games in multi-party healthcare coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
\insertmydocument{chapter}{How courts should respond to the stories defendants tell: A Bayesian account of a Dutch ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
\insertmydocument{chapter}{The spaces and places of argumentation: Developing a spatial model of argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
\insertmydocument{chapter}{Aggressiveness as a qualifier of dissent in interpersonal arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59

@@

\insertmydocument{chapter}{Be reasonable! Ways to react to cases of presumed unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65

@@

\insertmydocument{chapter}{A decision tree for annotating argumentation scheme corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71

@@

\insertmydocument{chapter}{Strategic manoeuvring with the construction “We know that X” in parliamentary debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

@@

\insertmydocument{chapter}{Holism of reasons and its consequences for argumentation theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The text structure and discourse of disagreement in Irish letters to the editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81

@@

\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: organ and tissue donation, public trust, the voice of dissent and informed consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
\insertmydocument{chapter}{“The worst ever conceived by a man of genius. ” Hume’s probability argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92

@@

\insertmydocument{chapter}{The rhetorical potential of metaphor: An experimental study on the effect of metaphors in argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98

@@

\insertmydocument{chapter}{Multimodal argumentation and dissent – a perspective of multimodal critical discourse analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111

@@

\insertmydocument{chapter}{Detecting and handling disagreement in multi-party health coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116

@@

\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
\insertmydocument{chapter}{Conductive Arguments. Towards a solution of the riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
\insertmydocument{chapter}{A ludological perspective on the shape of argument: Collaborative assent to dissenting opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
\insertmydocument{chapter}{Towards the justification of warrant in a legal hard case: How to justify a legal rule by the backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127

@@

\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The prospects for multimodal schemes of argument: Assessing Adbusters’ spoofing strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
\insertmydocument{chapter}{(Mis)framing photographs as an obstacle to fair dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five approaches to argument strength: probabilistic, dialectical, structural, empirical, and computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From dialogic to argument-based teaching: Significant teacher moves in framing classroom-based argumentation dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

>>>>

\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}

\insertmydocument{chapter}{Is There an Informal Logic Approach to Argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}

\insertmydocument{chapter}{Structural Differences Between Practical and Cognitive Presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural Differences Between Practical and Cognitive Presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}

@@

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}

@@

\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}

@@

\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}

@@

\insertmydocument{chapter}{Speech Act Pluralism in Argumentative Polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}

\insertmydocument{chapter}{Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}

\insertmydocument{chapter}{Arguments From Expert Opinion – An Epistemological Approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}

\insertmydocument{chapter}{All-out Attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}

@@

\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}

@@

\insertmydocument{chapter}{Strange Fish: Belief and the Roots of Disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
\insertmydocument{chapter}{An optimistic perspective on deep disagreement? Commentary on Tindale’s Strange Fish: Belief and the Roots of Disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}

\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}

@@

\insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3

@@

\insertmydocument{chapter}{The Role of Reasoning and Arguing in Youth Democratic Participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
\insertmydocument{chapter}{Pictures and Reasoning: Visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
\insertmydocument{chapter}{Issues Leading to Argumentative Discussions During Family Mealtime Conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
\insertmydocument{chapter}{Value-based Argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16

@@

\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19

@@

\insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23

@@

\insertmydocument{chapter}{Arguing Brexit on Twitter: A Corpus Linguistic Study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
\insertmydocument{chapter}{Protagoras’ Principles, Disagreement and the Possibility of Error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
\insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
\insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
\insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36

@@

\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
\insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44

@@

\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47

@@

\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
\insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
\insertmydocument{chapter}{The Spaces and Places of Argumentation: Developing a Spatial Model of Argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
\insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59

@@

\insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65

@@

\insertmydocument{chapter}{A Decision Tree for Annotating Argumentation Scheme Corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71

@@

\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

@@

\insertmydocument{chapter}{Holism of Reasons and its Consequences for Argumentation Theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The Text Structure and Discourse of Disagreement in Irish letters to the Editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81

@@

\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: Organ and Tissue Donation, Public Trust, the Voice of Dissent and Informed Consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
\insertmydocument{chapter}{“The worst ever conceived by a man of genius. ” Hume’s Probability Argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92

@@

\insertmydocument{chapter}{The Rhetorical Potential of Metaphor: An Experimental Study on the Effect of Metaphors in Argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
\insertmydocument{chapter}{Separate Opinions as an Argumentative Activity Type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98

@@

\insertmydocument{chapter}{Multimodal Argumentation and Dissent -- a Perspective of Multimodal Critical Discourse Analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111

@@

\insertmydocument{chapter}{Detecting and Handling Disagreement in Multi-party Health Coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
\insertmydocument{chapter}{Explaining Away and the Propensity Interpretation of Probability: the Case of Unequal Priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116

@@

\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval Reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
\insertmydocument{chapter}{Conductive Arguments. Towards a Solution of the Riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
\insertmydocument{chapter}{A Ludological Perspective on the Shape of Argument: Collaborative Assent to Dissenting Opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
\insertmydocument{chapter}{Towards the Justification of Warrant in a Legal Hard Case: How to Justify a Legal Rule by the Backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127

@@

\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
